Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-01-26 paper/paper.tex
first complete discussion

\section{Discussion}
Relevant structure in brain imaging data has long been
separately investigated
along two distinct organizational principles:
functional segregation into discrete brain regions
and functional integration by inter-regional brain networks.
%
This paper demonstrates the simultaneous exploitation of
both these neurobiological compartments
for sparse variable selection and high-dimensional prediction.
%
Introducing existing domain knowledge into model selection
naturally priviledges model hypotheses in the function space
that are most neurobiologically plausible.
%
The neurobiologically informed
hierarchical structured sparsity penalty is shown to enhance
model interpretability and generalization performance,
although these statistical goals are typically in conflict.

1) each voxel
We assume regions and networks but can estimate 
importance of each voxel.
neurobiologically motivated restrictions to
complexity circumvented the curse of dimensionality and allowed
for useful, simplified views on brain function.
previously laborious feature engineering / selection procedures

2) restrictions to complexity according to neurobiological facts
-> bias-variance tradeoff: negigible increase in bias but large decrease in variance
-> VC: decrease complexitiy capactiy -> better chance for generalization out of sample

guide model selection

3)
multiple comparisons problem has the curse of dimensionality
as its close correspondence in statistical learning
sparsity -> solves the curse at the estimation level

4) region-constrained or network-constrained model estimation
can lead to similar predictive performance

In the future,
the proposed regularization scheme can be used for various
learning tasks in systems neuroscience.
This includes supervised classification and regression
with one or several target variables.
%
Region-network sparsity priors could even be used to inform
unsupervised statistical estimators,
including principal component analysis
\cite{jenatton2009structured}
and
k-means clustering \cite{???}.
%
Additionally,
the structured sparsity penalty could be extended
from the spatial domain of neural activity to
spatiotemporally coherent neural activity patterns
\cite{gramfort2011tracking}.
%
Ultimately,
successful high-dimensional inference is
an important prerequisite
for prediction of diagnosis,
disease trajectories, and treatment responses
for personalized medicine in psychiatry and neurology
\cite{gabrieli2015prediction}.

>>>>

\section{Discussion}
Relevant structure in brain imaging data has long been investigated
separately
according to two distinct organizational principles:
functional segregation into discrete brain regions
and functional integration by interregional brain networks.
%
This paper demonstrates the simultaneous exploitation of
both these neurobiological compartments
for sparse variable selection and high-dimensional prediction
in a reference dataset.
%
Introducing existing domain knowledge into model selection
allowed privileging members of the function space
that are most neurobiologically plausible.
%
Domain-informed hierarchical structured sparsity is shown to enhance
both model interpretability and generalization performance,
although these statistical-learning goals are typically in conflict.

The present approach has important advantages over previous
neuroimaging studies that capitalized on dimensionality reduction to harness
the curse of dimensionality.
They often used preliminary region-wise pooling functions
or regression against network templates
for subsequent supervised learning on the aggregated feature space.
Such two-step approaches of feature engineering and inference
\textit{i)} can only account for either functional specialization or
functional integration of brain organization,
\textit{ii)} depend on the ground truth being a region or network effect,
and
\textit{iii)} cannot issue individual coefficients for every brain voxels.
%
Hierarchical region-network sparsity overcomes these shortcomings
by estimating individual voxel contributions
while benefitting from their functional segregation and integration
to restrict statistical complexity.
%
Viewed from the bias-variance tradeoff,
our modification to logistic regression estimators
entailed a large decrease in model variance but only a modest
increase in model bias.
Viewed from the Vapnik-Chervonenkis dimensions,
this entailed a healthy decrease in the complexity capactity of the prediction model
with a higher chance of generalizing to unobserved data.

In the future,
region-network sparsity priors could be incorporated into various
pattern-learning methods in systems neuroscience.
%
This includes supervised methods for whole-brain classification and regression
with one or several target variables.
The principled regularization scheme could even inform
unsupervised structure discovery methods,
such as principal component analysis
\cite{jenatton2009structured}
and
k-means clustering \cite{witten2010framework}.
%
Additionally,
model regularization by hierarchical structured sparsity could be extended
from the spatial domain of neural activity to
priors of coherent spatiotemporal activity structure
\cite{gramfort2011tracking}.
%
Ultimately,
successful high-dimensional inference is
an important prerequisite
for predicting diagnosis,
disease trajectories, and treatment responses
in personalized psychiatry and neurology.
